Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Small corrections:

```{r FigG1, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}

@@

## Figure
Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article.

@@

### Sex-bias in traits: Methods and results

>>>>

```{r FigG1, echo = FALSE, fig.width = 4, fig.height = 8, fig.cap="Workflow of data process and meta-analysis"}

@@

## Figure
Figure \@ref(fig:FigS1) is similar to Figure 3 in the main article except that lnVR has been added to the plot for comparison with lnCVR and lnRR.

@@

### Sex-bias in traits sub-analysis
